---
title: "Binary Regression Models"
author: "Zachary McCaw"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Binary Regression Regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=T, warning=F, message=F, cache=F, results='hold');
```

## Contents

* [Introduction](#introduction)
* [Logistic](#logistic)
* [Probit](#probit)
* [Robit](#robit)

# Introduction

This package provides implementations of regression models for a binary outcome. Throughout denote the outcome $y_{i}\in\{0,1\}$, the covariates $x_{i}\in\mathbb{R}^{p}$, and the linear predictor $\eta_{i} = x_{i}'\beta$.

# Logistic

## Model

In logistic regression, the latent variable $z_{i}$ follows a logistic distribution with center $\eta_{i}$ and unit scale:

$$
z_{i}|x_{i} \sim \text{Logistic}\big(\eta_{i},1) \\
y_{i} = I[z_{i}>0]
$$

## Implementation

Below, data are simulated for $n=10^{3}$ subjects. The linear predictor depends on four independent, standard normal covariates. The function `rBinReg` is provided for simulating from binary regression models. The function `fit.BinReg` with `model="logistic"` specifies a logistic model. 

```{r}
set.seed(100);
library(BinReg);
# Subjects
n = 1e3;
# Design matrix
X = matrix(rnorm(n=4*n),nrow=n);
# Regression coefficient
b = c(1,-0.5,-0.5,0);
# Logistic outcome
y = rBinReg(X,b,model="logistic");
# Estimate regression parameters
M = fit.BinReg(y=y,X=X,model="logistic");
show(M);
```

# Probit

## Model

In probit regression, the latent variable $z_{i}$ follows a normal distribution with center $\eta_{i}$ and unit scale:

$$
z_{i}|x_{i} \sim N\big(\eta_{i},1) \\
y_{i} = I[z_{i}>0]
$$

## Implementation

The function `fit.BinReg` with `model="probit"` specifies a probit model. 

```{r}
# Probit outcome
y = rBinReg(X,b,model="probit");
# Estimate regression parameters
M = fit.BinReg(y=y,X=X,model="probit");
show(M);
```

# Robit

## Model

In robit regression, the latent variable $z_{i}$ follows a $t_{\nu}$ distribution with center $\eta_{i}$, unit scale, and specified degrees of freedom $\nu$:

$$
z_{i}|x_{i} \sim t_{\nu}(\eta_{i}) \\
y_{i} = I[z_{i}>0]
$$

## Implementation

The function `fit.BinReg` with `model="robit"` specifies a robit model. 

```{r}
# Degrees of freedom
df = 7;
# Robit outcome
y = rBinReg(X,b,model="robit",df=df);
# Recover regression parameters
M = fit.BinReg(y=y,X=X,model="robit",df=df);
show(M);
```